A Hexagon Tile Map Algorithm for Displaying Spatial Data

### 2020-11-18 kobakian-cook.Rmd
complete changes recommended by Earl

The algorithm is implemented in the `sugarbag` package for R, this is the common name for the *Trigona carbonaria* bee species. Native to northern and eastern Australia this stingless species builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH]. This hive design inspired the use of multiple focal points in the algorithm, individual spirals are constructed by building out from various points on the geographic map base.

The result of the algorithm on rates of thyroid cancer for females in each of the SA2 areas of Australia is shown in figure \ref{fig:hexmap}.
The difference to the choropleth map in figure \ref{fig:choro} are clear. Now the thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible. Interestingly there is no clear divide between rural and urban SA2 areas as many rural areas, and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid cancer diagnosis for females. The hexagon tile map display provides a more accurate representation of the spatial distribution of thyroid cancer incidence across Australia.

When the algorithm is applied to the complete set of all Australian Statistical Areas at Level 2 it results in the hexagon tile map display shown in figure \ref{fig:hexmap}. This display highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart. This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities. There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average. Brisbane also experiences higher than average rates of diagnosis, but has more orange than red. The females in the cities of Adelaide and Perth  show much lower rates of diagnosis.

Compared to the choropleth map display, the low rates in the rural Australian communities are no longer dominating the display. While the representative hexagons are still visible against the black background, the much lower than average rates in the Northern Territory are less noticeable.

@@

There are several key steps needed to create the hexagon tile map as described in the flow chart in figure \ref{fig:sugarbag_flow}. First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations. These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbag_flow}. Each centroid can then be allocated to an available hexagon location. The steps for the allocation process are detailed in the right column of figure \ref{fig:sugarbag_flow}. There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit. To make tessellated plots with the hexagon allocations, the point locations are converted into hexagon shapes.

@@

Only two inputs are necessary to begin the algorithm; the shape file, and the id variable. The id variable should uniquely identify each geographic unit in the shape file.

The centroids are derived from the shape file. The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided. The derived centroids are a necessary input for an appropriate grid to be constructed. Each grid point is located a hexagon size distance from the next closest point in all six directions. The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance. This buffer distance can be helpful to account for densely populated coastal areas, allowing the use of the sea for hexagon locations.

The centroid set and hexagon tile map grid are necessary for the allocation process. Additionally, a set of reference locations can be provided as focal points, such as the capital cities of states or countries. The algorithm will use the focal points to create the order of allocation, prioritising the closest centroid locations to the focal points. Alternatively, a user can specify the variable that should be used to determine the order for the allocation.

@@

Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas. However, these maps are not easy to create manually, especially as the number of areas increases. This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays. This allows map makers and data communicators to spend their time to choosing the most effective display.

The `sugarbag` package has been written for R software, it contains a set of functions that help R users to create a hexagon tile map. The algorithm presented in the `sugarbag` package operates on a set of simple feature geometry objects [@sf], this package allows R users to create `sf` objects by importing polygons stored in various formats. Users should provide a set of polygons that define geographic units by their administrative boundaries. The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of capital cities. The centroid location of each geographic unit is used to measure the proximity. It emphasises the capital cities as population hubs, rather than emphasizing the size of large, rural geographic units.

A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, these options may affect the speed of the creation. 
The hexagon size may need adjustments depending on the density of the population, users can provide an appropriate hexagon size and re-run the algorithm. The buffer distance may need to be increased if the coastal cities need to extend beyond the geographic land mass.

@@

and the development version can be install from the GitHub repository:

@@

The polygon set of Tasmania in 2011 is accessed from the `absmapsdata` package. A single column of the data set is used to identify the unique areas. In this case, the unique SA2 names for each SA2 have been used.

@@

Not all of the grid points will be used, especially if islands result in a large grid space. To filter the grid for appropriate hexagon locations for allocation, the `create_grid` function will call the `create_buffer` function. It finds the grid points needed to best capture the set of centroids on a hexagon tile map. Reducing the buffer can help to decrease the amount of time taken, as there will be less points in the water to consider for each centroid allocation.

@@

If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded, only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
By default the angle filter for the hexagon grid points create plus and minus 30 degrees bounds of the angle from the focal point to the geographic centroid. This will increase if no points can be found within the `hex_filter` distance. The default angle of 30 was chosen to allow the algorithm to find hexagons that best maintained the spatial relationship between the focal point and geographic centroid.

@@

Creating an animation connecting these two displays can allow users t grasp the meaning of the connected hexagons. It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations. The rapid decrease in size of the large rural areas can show how large the landmass of Statistical Areas can be, and how few people occupy rural areas. The `gganimate` [@gganimate] package can be used to make an animation. It connects the polygons for each area in the two displays using the `sf_id` variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.

## Conclusion {#conclusion-03}

@@

<!-- implementation -->
The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important. This solution uses equally sized areas, and maintain neighbourhood boundary connections. The `sugarbag` package for `R` automates the creation of tessellated hexagon tile maps by providing an algorithm to design these displays. The Australian application preserves spatial relationships, and emphasises capital cities. 
However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable. The algorithm is heavily dependent on the focal points used, as this determines the order of allocation. With careful consideration of the choropleth map, the small geographic inner city areas may have been noticed by viewers, but the hexagon tile map display emphasises them. The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons in New South Wales.

@@

This algorithm should be general enough to apply to other countries and related problems. The algorithm has only been tested using single countries. While the buffer allows extension beyond the furthest centroids, there is no mechanism implemented to protect the borders and ensure centroids are placed within the geographic borders of a country.
The algorithm is also currently limited to representing each geographic area with only one hexagon. Future developments may address these limitations, and refine the filter steps for final selection of a hexagon grid point for each centroid. A direct angle is currently implemented, but may narrowly miss appropriate hexagons, a logarithmic function may help to choose a closer hexagon to the original centroid location.
This algorithm is an effective start to creating hexagon tile maps for many geographic units. This contributes to an extensive body of work that encourages the use of alternative map displays for statistical displays of spatial data.

>>>>

The algorithm is implemented in the `sugarbag` package for `R`, named after the common name for the *Trigona carbonaria* bee – a species which builds flat layers of hexagonal brood cells, spiralling out from a central point [@PH]. This unusual pattern also provided the inspiration for the algorithm, where the maps are constructed by building out from multiple focal points on the geographic map base in a spiral fashion.

The result of the algorithm applied to the same data represented in figure \ref{fig:choro} shows rates of thyroid cancer for females in each of the SA2 areas of Australia as hexagons in figure \ref{fig:hexmap}.
The difference to the choropleth map in figure \ref{fig:choro} are clear. Now the higher thyroid cancer incidence in the densely populated areas in Sydney, Brisbane and Perth are visible. Interestingly, there is no clear divide between rural and urban SA2 areas, as many rural areas and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of thyroid incidence for females. The hexagon tile map display provides a more accurate representation of the spatial distribution of thyroid cancer incidence across Australia.

Figure \ref{fig:hexmap} highlights the density of Australian capital cities, as it draws attention to the many communities in Sydney, Melbourne and Hobart. This display also highlights the disparity in the burden of thyroid cancer for females in the communities of these cities. There are several collections of red hexagons in Sydney that represent the communities with much higher rates of diagnosis than the Australian average. Brisbane also experiences higher than average rates of diagnosis, but has more orange than red. The females in the cities of Adelaide and Perth  show much lower rates of diagnosis.

Compared to the choropleth map display in figure \ref{fig:choro}, the low rates in the rural Australian communities are no longer dominating the display. While the representative hexagons are still visible against the black background, the much lower than average rates in rural Australia are less noticeable.

@@

There are several key steps in the creation of the hexagon tile map as described in the flow chart in figure \ref{fig:sugarbag_flow}. First, derive the set of centroids from the polygons provided, then create the grid of hexagon locations. These two processes are defined in the blue left column of the flow chart in figure \ref{fig:sugarbag_flow}. Each centroid can then be allocated to an available hexagon location. The steps for the allocation process are detailed in the right column of figure \ref{fig:sugarbag_flow}. There are several filter steps to speed the process of selecting an appropriate hexagon to represent each geographic unit. To make tessellated plots with the hexagon allocations, the point locations are converted into hexagon shapes.

@@

Only two inputs are necessary to begin the algorithm; the shapefile, and the ID variable. The ID variable should uniquely identify each geographic unit in the shapefile.

The centroids are derived from the shapefile. The amount of centroids within the geographic map is used to determine an appropriate hexagon size if one is not provided. The derived centroids are a necessary input for an appropriate grid to be constructed. Each grid point is located a hexagon size distance from the next closest point in all six directions. The grid will initially cover the entire map space, encompassing all the centroid locations and will extend in all directions to the extent of the buffer distance. This buffer distance can be helpful to account for densely populated coastal areas, allowing the hexagon locations to spread beyond the coastline, over the sea.

The centroid set and hexagon tile map grid are necessary for the allocation process. Additionally, a set of reference locations can be provided as focal points, typically compact and/or densely populated areas such as major cities. The algorithm will use the focal points to create the order of allocation, prioritising the closest centroid locations to the focal points. The user can also specify the variable that should be used to determine the order for the allocation.

@@

Hexagon tile maps can be useful to understand a distribution across a collection of geographic areas. However, these maps are not easy to create manually, especially as the number of areas increases. This algorithm was created to automate this process, and reduce the manual load involved in creating and implementing alternative displays. This allows map makers and data communicators to spend their time choosing the most effective display.

The `sugarbag` package contains a set of functions that help R users to create a hexagon tile map. The algorithm presented in the `sugarbag` package operates on a set of simple feature geometry objects , known as `sf` objects[@sf]. This package allows R users to create `sf` objects by importing polygons stored in various formats. Users should provide a set of polygons that define geographic units by their administrative boundaries. The functions arrange the geographic units in order of proximity to a set of locations provided, such as the centre of major cities. The centroid location of each geographic unit is used to measure the proximity. It emphasises the major cities as population hubs, rather than emphasizing the size of large, rural geographic units.

A user can tweak the parameters of the hexagon map using the additional arguments to the `create_hexmap` function, but these options may affect the speed of the algorithm. 
The hexagon size may need adjustments depending on the density of the population; users can provide an appropriate hexagon size and re-run the algorithm. The buffer distance may need to be increased if the coastal cities need to extend beyond the geographic land mass.

@@

and the development version can be installed from the GitHub repository:

@@

The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s, is accessed from the `absmapsdata` package. A single column of the data set is used to identify the unique areas. In this case, the unique SA2 names for each SA2 have been used.

@@

Not all of the grid points will be used, especially if islands result in a large grid space. To filter the grid for appropriate hexagon locations for allocation, the `create_grid` function will call the `create_buffer` function. It finds the grid points needed to best capture the set of centroids on a hexagon tile map. Reducing the buffer can help to decrease the amount of time taken, as there will be less points over the water to consider for each centroid allocation.

@@

If no available hexagon grid point is found within the original filter distance and angle, the distance is expanded and only when a maximum distance is reached will the angle expand to accommodate more possible grid points.
By default the angle filter for the hexagon grid points create plus and minus 30 degree bounds of the angle from the focal point to the geographic centroid. This will increase if no points can be found within the `hex_filter` distance. The default angle of 30 was chosen to allow the algorithm to find hexagons that best maintained the spatial relationship between the focal point and geographic centroid.

@@

Creating an animation connecting these two displays can allow users to grasp the meaning of the connected hexagons. It will also highlight the density of the communities using the rapid expansion of the inner-city areas, these hexagons will move the furthest and will move rapidly in the animation from their geographic locations. The rapid decrease in size of the large rural areas can show the large size of their collective landmass. The `gganimate` [@gganimate] package can be used to make an animation. It connects the polygons for each area in the two displays using the `sf_id` variable, the names of the statistical areas, and creates intermediate displays as they geographic areas shrink or expand to the chosen hexagon size.

## Discussion and Conclusion {#conclusion-03}

@@

<!-- implementation -->
The hexagon tile map display acknowledges that the amount of residents can differ but each administrative area is equally important. This solution uses equally sized areas, and maintain neighbourhood boundary connections. The `sugarbag` package for `R` automates the creation of tessellated hexagon tile maps by providing an algorithm to design these displays. The Australian application preserves spatial relationships, and emphasises capital cities. 
However, similar to the choropleth map display the tessellation does not allow the size of the hexagons to represent another variable. The algorithm is heavily dependent on the focal points used, as this determines the order of allocation. With careful consideration of the choropleth map, the small geographic inner city areas may not have been noticed by viewers, but the hexagon tile map display emphasises them. The communities in northern Tasmania and the Northern territory do not draw attention because of their size as in the choropleth, but their colour is still noticeably below average when contrasted with the hexagons in New South Wales.

@@

This algorithm should be general enough to apply to other study regions and contexts. The algorithm has only been tested using single countries. While the buffer allows extension beyond the furthest centroids, there is no mechanism implemented to protect the borders and ensure centroids are placed within the geographic borders of a country.
The algorithm is also currently limited to representing each geographic area with only one hexagon. Future developments may address these limitations, and refine the filter steps for final selection of a hexagon grid point for each centroid. A direct angle is currently implemented, but may narrowly miss appropriate hexagons, a logarithmic function may help to choose a closer hexagon to the original centroid location.
This algorithm is an effective start to creating hexagon tile maps for many geographic units. This contributes to an extensive body of work that encourages the use of alternative map displays for statistical displays of spatial data.

### 2020-11-18 kobakian-cook.tex
complete changes recommended by Earl

The algorithm is implemented in the \texttt{sugarbag} package for R,
this is the common name for the \emph{Trigona carbonaria} bee species.
Native to northern and eastern Australia this stingless species builds
flat layers of hexagonal brood cells, spiralling out from a central
point \citep{PH}. This hive design inspired the use of multiple focal
points in the algorithm, individual spirals are constructed by building
out from various points on the geographic map base.

The result of the algorithm on rates of thyroid cancer for females in
each of the SA2 areas of Australia is shown in figure \ref{fig:hexmap}.
The difference to the choropleth map in figure \ref{fig:choro} are
clear. Now the thyroid cancer incidence in the densely populated areas
in Sydney, Brisbane and Perth are visible. Interestingly there is no
clear divide between rural and urban SA2 areas as many rural areas, and
the cities of Melbourne, Darwin, Adelaide and Hobart have low rates of
thyroid cancer diagnosis for females. The hexagon tile map display
provides a more accurate representation of the spatial distribution of
thyroid cancer incidence across Australia.

When the algorithm is applied to the complete set of all Australian
Statistical Areas at Level 2 it results in the hexagon tile map display
shown in figure \ref{fig:hexmap}. This display highlights the density of
Australian capital cities, as it draws attention to the many communities
in Sydney, Melbourne and Hobart. This display also highlights the
disparity in the burden of thyroid cancer for females in the communities
of these cities. There are several collections of red hexagons in Sydney
that represent the communities with much higher rates of diagnosis than
the Australian average. Brisbane also experiences higher than average
rates of diagnosis, but has more orange than red. The females in the
cities of Adelaide and Perth show much lower rates of diagnosis.

Compared to the choropleth map display, the low rates in the rural
Australian communities are no longer dominating the display. While the
representative hexagons are still visible against the black background,
the much lower than average rates in the Northern Territory are less
noticeable.

@@

Hexagon tile maps can be useful to understand a distribution across a
collection of geographic areas. However, these maps are not easy to
create manually, especially as the number of areas increases. This
algorithm was created to automate this process, and reduce the manual
load involved in creating and implementing alternative displays. This
allows map makers and data communicators to spend their time to choosing
the most effective display.

The \texttt{sugarbag} package has been written for R software, it
contains a set of functions that help R users to create a hexagon tile
map. The algorithm presented in the \texttt{sugarbag} package operates
on a set of simple feature geometry objects \citep{sf}, this package
allows R users to create \texttt{sf} objects by importing polygons
stored in various formats. Users should provide a set of polygons that
define geographic units by their administrative boundaries. The
functions arrange the geographic units in order of proximity to a set of
locations provided, such as the centre of capital cities. The centroid
location of each geographic unit is used to measure the proximity. It
emphasises the capital cities as population hubs, rather than
emphasizing the size of large, rural geographic units.

A user can tweak the parameters of the hexagon map using the additional
arguments to the \texttt{create\_hexmap} function, these options may
affect the speed of the creation. The hexagon size may need adjustments
depending on the density of the population, users can provide an
appropriate hexagon size and re-run the algorithm. The buffer distance
may need to be increased if the coastal cities need to extend beyond the
geographic land mass.

@@

The polygon set of Tasmania in 2011 is accessed from the
\texttt{absmapsdata} package. A single column of the data set is used to
identify the unique areas. In this case, the unique SA2 names for each
SA2 have been used.

@@

Not all of the grid points will be used, especially if islands result in
a large grid space. To filter the grid for appropriate hexagon locations
for allocation, the \texttt{create\_grid} function will call the
\texttt{create\_buffer} function. It finds the grid points needed to
best capture the set of centroids on a hexagon tile map. Reducing the
buffer can help to decrease the amount of time taken, as there will be
less points in the water to consider for each centroid allocation.

@@

If no available hexagon grid point is found within the original filter
distance and angle, the distance is expanded, only when a maximum
distance is reached will the angle expand to accommodate more possible
grid points. By default the angle filter for the hexagon grid points
create plus and minus 30 degrees bounds of the angle from the focal
point to the geographic centroid. This will increase if no points can be
found within the \texttt{hex\_filter} distance. The default angle of 30
was chosen to allow the algorithm to find hexagons that best maintained
the spatial relationship between the focal point and geographic
centroid.

@@

Creating an animation connecting these two displays can allow users t
grasp the meaning of the connected hexagons. It will also highlight the
density of the communities using the rapid expansion of the inner-city
areas, these hexagons will move the furthest and will move rapidly in
the animation from their geographic locations. The rapid decrease in
size of the large rural areas can show how large the landmass of
Statistical Areas can be, and how few people occupy rural areas. The
\texttt{gganimate} \citep{gganimate} package can be used to make an
animation. It connects the polygons for each area in the two displays
using the \texttt{sf\_id} variable, the names of the statistical areas,
and creates intermediate displays as they geographic areas shrink or
expand to the chosen hexagon size.

\hypertarget{conclusion-03}{%
\subsection{Conclusion}\label{conclusion-03}}

@@

The hexagon tile map display acknowledges that the amount of residents
can differ but each administrative area is equally important. This
solution uses equally sized areas, and maintain neighbourhood boundary
connections. The \texttt{sugarbag} package for \texttt{R} automates the
creation of tessellated hexagon tile maps by providing an algorithm to
design these displays. The Australian application preserves spatial
relationships, and emphasises capital cities. However, similar to the
choropleth map display the tessellation does not allow the size of the
hexagons to represent another variable. The algorithm is heavily
dependent on the focal points used, as this determines the order of
allocation. With careful consideration of the choropleth map, the small
geographic inner city areas may have been noticed by viewers, but the
hexagon tile map display emphasises them. The communities in northern
Tasmania and the Northern territory do not draw attention because of
their size as in the choropleth, but their colour is still noticeably
below average when contrasted with the hexagons in New South Wales.

This algorithm should be general enough to apply to other countries and
related problems. The algorithm has only been tested using single
countries. While the buffer allows extension beyond the furthest
centroids, there is no mechanism implemented to protect the borders and
ensure centroids are placed within the geographic borders of a country.
The algorithm is also currently limited to representing each geographic
area with only one hexagon. Future developments may address these
limitations, and refine the filter steps for final selection of a
hexagon grid point for each centroid. A direct angle is currently
implemented, but may narrowly miss appropriate hexagons, a logarithmic
function may help to choose a closer hexagon to the original centroid
location. This algorithm is an effective start to creating hexagon tile
maps for many geographic units. This contributes to an extensive body of
work that encourages the use of alternative map displays for statistical
displays of spatial data.

>>>>

The algorithm is implemented in the \texttt{sugarbag} package for
\texttt{R}, named after the common name for the \emph{Trigona
carbonaria} bee -- a species which builds flat layers of hexagonal brood
cells, spiralling out from a central point \citep{PH}. This unusual
pattern also provided the inspiration for the algorithm, where the maps
are constructed by building out from multiple focal points on the
geographic map base in a spiral fashion.

The result of the algorithm applied to the same data represented in
figure \ref{fig:choro} shows rates of thyroid cancer for females in each
of the SA2 areas of Australia as hexagons in figure \ref{fig:hexmap}.
The difference to the choropleth map in figure \ref{fig:choro} are
clear. Now the higher thyroid cancer incidence in the densely populated
areas in Sydney, Brisbane and Perth are visible. Interestingly, there is
no clear divide between rural and urban SA2 areas, as many rural areas
and the cities of Melbourne, Darwin, Adelaide and Hobart have low rates
of thyroid incidence for females. The hexagon tile map display provides
a more accurate representation of the spatial distribution of thyroid
cancer incidence across Australia.

Figure \ref{fig:hexmap} highlights the density of Australian capital
cities, as it draws attention to the many communities in Sydney,
Melbourne and Hobart. This display also highlights the disparity in the
burden of thyroid cancer for females in the communities of these cities.
There are several collections of red hexagons in Sydney that represent
the communities with much higher rates of diagnosis than the Australian
average. Brisbane also experiences higher than average rates of
diagnosis, but has more orange than red. The females in the cities of
Adelaide and Perth show much lower rates of diagnosis.

Compared to the choropleth map display in figure \ref{fig:choro}, the
low rates in the rural Australian communities are no longer dominating
the display. While the representative hexagons are still visible against
the black background, the much lower than average rates in rural
Australia are less noticeable.

@@

Hexagon tile maps can be useful to understand a distribution across a
collection of geographic areas. However, these maps are not easy to
create manually, especially as the number of areas increases. This
algorithm was created to automate this process, and reduce the manual
load involved in creating and implementing alternative displays. This
allows map makers and data communicators to spend their time choosing
the most effective display.

The \texttt{sugarbag} package contains a set of functions that help R
users to create a hexagon tile map. The algorithm presented in the
\texttt{sugarbag} package operates on a set of simple feature geometry
objects , known as \texttt{sf} objects\citep{sf}. This package allows R
users to create \texttt{sf} objects by importing polygons stored in
various formats. Users should provide a set of polygons that define
geographic units by their administrative boundaries. The functions
arrange the geographic units in order of proximity to a set of locations
provided, such as the centre of major cities. The centroid location of
each geographic unit is used to measure the proximity. It emphasises the
major cities as population hubs, rather than emphasizing the size of
large, rural geographic units.

A user can tweak the parameters of the hexagon map using the additional
arguments to the \texttt{create\_hexmap} function, but these options may
affect the speed of the algorithm. The hexagon size may need adjustments
depending on the density of the population; users can provide an
appropriate hexagon size and re-run the algorithm. The buffer distance
may need to be increased if the coastal cities need to extend beyond the
geographic land mass.

@@

The set of SA2 polygons for Tasmania, using the 2011 definition of SA2s,
is accessed from the \texttt{absmapsdata} package. A single column of
the data set is used to identify the unique areas. In this case, the
unique SA2 names for each SA2 have been used.

@@

Not all of the grid points will be used, especially if islands result in
a large grid space. To filter the grid for appropriate hexagon locations
for allocation, the \texttt{create\_grid} function will call the
\texttt{create\_buffer} function. It finds the grid points needed to
best capture the set of centroids on a hexagon tile map. Reducing the
buffer can help to decrease the amount of time taken, as there will be
less points over the water to consider for each centroid allocation.

@@

If no available hexagon grid point is found within the original filter
distance and angle, the distance is expanded and only when a maximum
distance is reached will the angle expand to accommodate more possible
grid points. By default the angle filter for the hexagon grid points
create plus and minus 30 degree bounds of the angle from the focal point
to the geographic centroid. This will increase if no points can be found
within the \texttt{hex\_filter} distance. The default angle of 30 was
chosen to allow the algorithm to find hexagons that best maintained the
spatial relationship between the focal point and geographic centroid.

@@

Creating an animation connecting these two displays can allow users to
grasp the meaning of the connected hexagons. It will also highlight the
density of the communities using the rapid expansion of the inner-city
areas, these hexagons will move the furthest and will move rapidly in
the animation from their geographic locations. The rapid decrease in
size of the large rural areas can show the large size of their
collective landmass. The \texttt{gganimate} \citep{gganimate} package
can be used to make an animation. It connects the polygons for each area
in the two displays using the \texttt{sf\_id} variable, the names of the
statistical areas, and creates intermediate displays as they geographic
areas shrink or expand to the chosen hexagon size.

\hypertarget{conclusion-03}{%
\subsection{Discussion and Conclusion}\label{conclusion-03}}

@@

The hexagon tile map display acknowledges that the amount of residents
can differ but each administrative area is equally important. This
solution uses equally sized areas, and maintain neighbourhood boundary
connections. The \texttt{sugarbag} package for \texttt{R} automates the
creation of tessellated hexagon tile maps by providing an algorithm to
design these displays. The Australian application preserves spatial
relationships, and emphasises capital cities. However, similar to the
choropleth map display the tessellation does not allow the size of the
hexagons to represent another variable. The algorithm is heavily
dependent on the focal points used, as this determines the order of
allocation. With careful consideration of the choropleth map, the small
geographic inner city areas may not have been noticed by viewers, but
the hexagon tile map display emphasises them. The communities in
northern Tasmania and the Northern territory do not draw attention
because of their size as in the choropleth, but their colour is still
noticeably below average when contrasted with the hexagons in New South
Wales.

This algorithm should be general enough to apply to other study regions
and contexts. The algorithm has only been tested using single countries.
While the buffer allows extension beyond the furthest centroids, there
is no mechanism implemented to protect the borders and ensure centroids
are placed within the geographic borders of a country. The algorithm is
also currently limited to representing each geographic area with only
one hexagon. Future developments may address these limitations, and
refine the filter steps for final selection of a hexagon grid point for
each centroid. A direct angle is currently implemented, but may narrowly
miss appropriate hexagons, a logarithmic function may help to choose a
closer hexagon to the original centroid location. This algorithm is an
effective start to creating hexagon tile maps for many geographic units.
This contributes to an extensive body of work that encourages the use of
alternative map displays for statistical displays of spatial data.
